---
title: Schedule
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(kableExtra);library(stringr); library(pander)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# Last Updated: `r format(Sys.time(), "%a %b %d %X")` {.tabset .tabset-fade .tabset-pills}

**SPRING 23 Updates in progress**

## Overview

<p>
Unless specified otherwise, all assignments are due at midnight on the due date listed.  

Don't forget to check the weekly details (and Canvas) for information on how to prepare and links to other materials.   

**PMA6**: Practical Multivariate Analysis 6th edition  
**ASCN**: Applied Stats Course Notes (linked in nav bar under Materials)
</p>
```{r}
# Read in schedule
rawdat <- read_xlsx("schedule_456.xlsx", sheet='weekly_schedule')

# Set semester start date and format weeks nicely
start.date <- as.Date("2023-01-23")

# which rows have week numbers 
wn <- c(which(!is.na(rawdat$wknum))) %>% sort() 

# generate list of weekdates
wkdt <- seq.Date(start.date, start.date+7*16, by='week')

# format for display
weekdates <- paste0("Week ", rawdat$wknum[wn], " (", format(wkdt, "%m/%d") , ")") 
weekdates[9] <- "Spring Break (03/16)"
weekdates[17] <- "Finals Week (05/12)"

# Filter columns to display on schedule
out <- rawdat %>% select(Topic:Assignments)

# add bold to due dates
out$Assignments <- gsub(" (", " (<b>", out$Assignments, fixed=TRUE)
out$Assignments <- gsub(" )", "</b>)", out$Assignments, fixed=TRUE)
out$Quiz <- gsub(" (", " (<b>", out$Quiz, fixed=TRUE)
out$Quiz <- gsub(" )", "</b>)", out$Quiz, fixed=TRUE)

wk.labs <-  "background-color: #4d6600; color: #fff;"
hlt.wks <-  "background-color: #754b13; color: #fff;"
```

```{r, results='asis'}
out %>% 
  kable(align="lccclc", escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>% 
  pack_rows(weekdates[1], wn[1],  wn[2]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[2], wn[2],  wn[3]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[3], wn[3],  wn[4]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[4], wn[4],  wn[5]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[5], wn[5],  wn[6]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[6], wn[6],  wn[7]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[7], wn[7],  wn[8]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[8], wn[8],  wn[9]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[9], wn[9],  wn[10]-1, label_row_css =hlt.wks) %>%
  pack_rows(weekdates[10], wn[10],  wn[11]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[11], wn[11],  wn[12]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[12], wn[12],  wn[13]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[13], wn[13],  wn[14]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[14], wn[14],  wn[15]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[15], wn[15],  wn[16]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[16], wn[16],  wn[17]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[17], wn[17],  wn[17], label_row_css =hlt.wks) %>%
  column_spec(1, width = "25%") %>% 
  column_spec(2, width = "15%") %>%
  column_spec(3, width = "10%") %>%
  column_spec(4, width = "35%") 
```

## Details

Click each link to expand or contract the details for that week. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Read in schedule
raw_detail <- read_excel("schedule_456.xlsx", sheet="slo_detail")

# Function to extract week and display data
details <- function(w){
  wd <- filter(raw_detail, wk==w) %>% 
        select(Topics, SLO, Prepare, Monday, Wednesday, Friday)  
  # strip data columns into separate lists
  Topic <- gsub("\r\n", "", wd$Topics)
  SLO  <- as.list(str_split(wd$SLO, "\r\n", simplify=TRUE))
  prep <- as.list(str_split(wd$Prepare, "\r\n", simplify=TRUE))
  mon  <- as.list(str_split(wd$Monday, "\r\n", simplify=TRUE))
  wed  <- as.list(str_split(wd$Wednesday, "\r\n", simplify=TRUE))
  fri  <- as.list(str_split(wd$Friday, "\r\n", simplify=TRUE))
 
  return(list(Topic=Topic, SLO=SLO, prep=prep, mon=mon, wed=wed, fri=fri))
}
```

```{r}
w1 <- details(1)
```
### <a href="#week1" data-toggle="collapse">Week 1: `r w1$Topic`</a>
<div id="week1" class="collapse">

#### Learning Objectives
By the end of the week, learners will be able to: 
```{r}
pander(w1$SLO)
```

#### How to prepare
```{r}
pander(w1$prep)
```

#### Monday overview
```{r}
pander(w1$mon)
```

#### Wednesday overview
```{r}
pander(w1$wed)
```

#### Friday overview
```{r}
pander(w1$fri)
```

</div>



```{r}
w2 <- details(2)
```
### <a href="#week2" data-toggle="collapse">Week 2: `r w2$Topic`</a>
<div id="week2" class="collapse">

#### Learning Objectives
```{r}
pander(w2$SLO)
```

#### How to prepare
```{r}
pander(w2$prep)
```

#### Monday overview
```{r}
pander(w2$mon)
```

#### Wednesday overview
```{r}
pander(w2$wed)
```

#### Friday overview
```{r}
pander(w2$fri)
```

</div>





```{r}
w3 <- details(3)
```

### <a href="#week3" data-toggle="collapse">Week 3: `r w3$Topic`</a>
<div id="week3" class="collapse">

#### Learning Objectives
```{r}
pander(w3$SLO)
```

#### How to prepare
```{r}
pander(w3$prep)
```

#### Monday overview
```{r}
pander(w3$mon)
```

#### Wednesday overview
```{r}
pander(w3$wed)
```

#### Friday overview
```{r}
pander(w3$fri)
```

</div>

```{r}
w4 <- details(4)
```
### <a href="#week4" data-toggle="collapse">Week 4: `r w4$Topic`</a>
<div id="week4" class="collapse">

#### Learning Objectives
```{r}
pander(w4$SLO)
```

#### How to prepare
```{r}
pander(w4$prep)
```

#### Monday overview
```{r}
pander(w4$mon)
```

#### Wednesday overview
```{r}
pander(w4$wed)
```

#### Friday overview
```{r}
pander(w4$fri)
```

</div>

```{r}
w5 <- details(5)
```
### <a href="#week5" data-toggle="collapse">Week 5: `r w5$Topic`</a>
<div id="week5" class="collapse">

#### Learning Objectives
```{r}
pander(w5$SLO)
```

#### How to prepare
```{r}
pander(w5$prep)
```

#### Monday overview
```{r}
pander(w5$mon)
```

#### Wednesday overview
```{r}
pander(w5$wed)
```

#### Friday overview
```{r}
pander(w5$fri)
```

</div>

```{r}
w6 <- details(6)
```
### <a href="#week6" data-toggle="collapse">Week 6: `r w6$Topic`</a>
<div id="week6" class="collapse">

#### Learning Objectives
```{r}
pander(w6$SLO)
```

#### How to prepare
```{r}
pander(w6$prep)
```

#### Monday overview
```{r}
pander(w6$mon)
```

#### Wednesday overview
```{r}
pander(w6$wed)
```

#### Friday overview
```{r}
pander(w6$fri)
```

</div>

```{r}
w7 <- details(7)
```
### <a href="#week7" data-toggle="collapse">Week 7: `r w7$Topic`</a>
<div id="week7" class="collapse">

#### Learning Objectives
```{r}
pander(w7$SLO)
```

#### How to prepare
```{r}
pander(w7$prep)
```

#### Monday overview
```{r}
pander(w7$mon)
```

#### Wednesday overview
```{r}
pander(w7$wed)
```

#### Friday overview
```{r}
pander(w7$fri)
```

</div>

```{r}
w8 <- details(8)
```

### <a href="#week8" data-toggle="collapse">Week 8: `r w8$Topic`</a>
<div id="week8" class="collapse">

#### Learning Objectives
```{r}
pander(w8$SLO)
```

#### How to prepare
```{r}
pander(w8$prep)
```

#### Monday overview
```{r}
pander(w8$mon)
```

#### Wednesday overview
```{r}
pander(w8$wed)
```

#### Friday overview
```{r}
pander(w8$fri)
```

</div>



```{r}
w9 <- details(9)
```
### <a href="#week9" data-toggle="collapse">Week 9: `r w9$Topic`</a>
<div id="week9" class="collapse">

#### Learning Objectives
```{r}
pander(w9$SLO)
```

#### How to prepare
```{r}
pander(w9$prep)
```

#### Monday overview
```{r}
pander(w9$mon)
```

#### Wednesday overview
```{r}
pander(w9$wed)
```

#### Friday overview
```{r}
pander(w9$fri)
```

</div>


```{r}
w10 <- details(10)
```

### <a href="#week10" data-toggle="collapse">Week 10: `r w10$Topic`</a>
<div id="week10" class="collapse">

#### Learning Objectives
```{r}
pander(w10$SLO)
```

#### How to prepare
```{r}
pander(w10$prep)
```

#### Monday overview
```{r}
pander(w10$mon)
```

#### Wednesday overview
```{r}
pander(w10$wed)
```

#### Friday overview
```{r}
pander(w10$fri)
```

</div>


```{r}
w11 <- details(11)
```

### <a href="#week11" data-toggle="collapse">Week 11: `r w11$Topic`</a>
<div id="week11" class="collapse">

#### Learning Objectives
```{r}
pander(w11$SLO)
```

#### How to prepare
```{r}
pander(w11$prep)
```

#### Monday overview
```{r}
pander(w11$mon)
```

#### Wednesday overview
```{r}
pander(w11$wed)
```

#### Friday overview
```{r}
pander(w11$fri)
```

</div>



```{r}
w12 <- details(12)
```
### <a href="#week12" data-toggle="collapse">Week 12: `r w12$Topic`</a>
<div id="week12" class="collapse">

#### Learning Objectives
```{r}
pander(w12$SLO)
```

#### How to prepare
```{r}
pander(w12$prep)
```

#### Monday overview
```{r}
pander(w12$mon)
```

#### Wednesday overview
```{r}
pander(w12$wed)
```

#### Friday overview
```{r}
pander(w12$fri)
```

</div>



```{r}
w13 <- details(13)
```
### <a href="#week13" data-toggle="collapse">Week 13: `r w13$Topic`</a>
<div id="week13" class="collapse">

#### Learning Objectives
```{r}
pander(w13$SLO)
```

#### How to prepare
```{r}
pander(w13$prep)
```

#### Monday overview
```{r}
pander(w13$mon)
```

#### Wednesday overview
```{r}
pander(w13$wed)
```

#### Friday overview
```{r}
pander(w13$fri)
```

</div>



```{r}
w14 <- details(14)
```
### <a href="#week14" data-toggle="collapse">Week 14: `r w14$Topic`</a>
<div id="week14" class="collapse">

#### Learning Objectives
```{r}
pander(w14$SLO)
```

#### How to prepare
```{r}
pander(w14$prep)
```

#### Monday overview
```{r}
pander(w14$mon)
```

#### Wednesday overview
```{r}
pander(w14$wed)
```

#### Friday overview
```{r}
pander(w14$fri)
```

</div>



```{r}
w15 <- details(15)
```
### <a href="#week15" data-toggle="collapse">Week 15: `r w15$Topic`</a>
<div id="week15" class="collapse">

#### Learning Objectives
```{r}
pander(w15$SLO)
```

#### How to prepare
```{r}
pander(w15$prep)
```

#### Monday overview
```{r}
pander(w15$mon)
```

#### Wednesday overview
```{r}
pander(w15$wed)
```

#### Friday overview
```{r}
pander(w15$fri)
```

</div>


