---
title: Weekly Activities
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(kableExtra);library(stringr); library(pander)

library(gt)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

```{r}
# Read in schedule
raw_slo_detail <- googlesheets4::read_sheet("1flUYEIAqLfa8Re4gNRTsRRA8skF4Ln6rImfKb-WDTZI", 
                                 sheet="slo_detail", 
                                 col_types = c("nDccccccc")) 

# Function to extract week and display data
details <- function(w){
  wd <- filter(raw_slo_detail, wk==w) %>% 
        select(Topics, SLO, Prepare, Monday, Wednesday, Friday)  
  # strip data columns into separate lists
  Topic <- gsub("\r\n", "", wd$Topics)
  SLO  <- as.list(str_split(wd$SLO, "\n", simplify=TRUE))
  prep <- as.list(str_split(wd$Prepare, "\n", simplify=TRUE))
  mon  <- as.list(str_split(wd$Monday, "\n", simplify=TRUE))
  wed  <- as.list(str_split(wd$Wednesday, "\n", simplify=TRUE))
  fri  <- as.list(str_split(wd$Friday, "\n", simplify=TRUE))
 
  return(list(Topic=Topic, SLO=SLO, prep=prep, mon=mon, wed=wed, fri=fri))
}

```

Click each link to expand or contract the details for that week. 

```{r}
w1 <- details(1)
```

### <a href="#week1" data-toggle="collapse">Week 1: `r w1$Topic`</a>
<div id="week1" class="collapse">

#### Learning Objectives
By the end of the week, learners will be able to: 
```{r}
pander(w1$SLO)
```

#### How to prepare
```{r}
pander(w1$prep)
```

#### Monday overview
```{r}
pander(w1$mon)
```

#### Wednesday overview
```{r}
pander(w1$wed)
```

#### Friday overview
```{r}
pander(w1$fri)
```

</div>


```{r}
w2 <- details(2)
```
### <a href="#week2" data-toggle="collapse">Week 2: `r w2$Topic`</a>
<div id="week2" class="collapse">

#### Learning Objectives
```{r}
pander(w2$SLO)
```

#### How to prepare
```{r}
pander(w2$prep)
```

#### Monday overview
```{r}
pander(w2$mon)
```

#### Wednesday overview
```{r}
pander(w2$wed)
```

#### Friday overview
```{r}
pander(w2$fri)
```

</div>

```{r}
w3 <- details(3)
```

### <a href="#week3" data-toggle="collapse">Week 3: `r w3$Topic`</a>
<div id="week3" class="collapse">

#### Learning Objectives
```{r}
pander(w3$SLO)
```

#### How to prepare
```{r}
pander(w3$prep)
```

#### Monday overview
```{r}
pander(w3$mon)
```

#### Wednesday overview
```{r}
pander(w3$wed)
```

#### Friday overview
```{r}
pander(w3$fri)
```

</div>


```{r}
w4 <- details(4)
```

### <a href="#week4" data-toggle="collapse">Week 4: `r w4$Topic`</a>
<div id="week4" class="collapse">

#### Learning Objectives
```{r}
pander(w4$SLO)
```

#### How to prepare
```{r}
pander(w4$prep)
```

#### Monday overview
```{r}
pander(w4$mon)
```

#### Wednesday overview
```{r}
pander(w4$wed)
```

#### Friday overview
```{r}
pander(w4$fri)
```

</div>
