---
output:
  html_document:
    highlight: tango
    theme: journal
    toc: yes
    toc_float: yes
css: css/style.css
title: "Week 1: Jan 22 - Jan 28"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(knitr)
library(kableExtra); library(stringr)
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```
<br>

_Last Updated: `r format(Sys.time(), "%a %b %d %X")` _
<br>


```{r echo=FALSE, message=FALSE, warning=FALSE}
raw <- read_excel("schedule_456.xlsx")
week.w <- filter(raw, Week==1)

topics <- str_split(week.w$Topics, ",", simplify=TRUE)
SLO    <- t(str_split(week.w$SLO, "\r\n", simplify=TRUE))
prep   <- t(str_split(week.w$Prepare, "\r\n", simplify=TRUE))
mats   <- t(str_split(week.w$Materials, "\r\n", simplify=TRUE))
hw     <- t(str_split(week.w$Assignments, "\r\n", simplify=TRUE))
mon    <- t(str_split(week.w$Monday, "\r\n", simplify=TRUE))
wed    <- t(str_split(week.w$Wednesday, "\r\n", simplify=TRUE))
fri    <- t(str_split(week.w$Friday, "\r\n", simplify=TRUE))
```

----

# Learning Objectives
```{r}
kable(SLO) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

# Prepare
```{r}
kable(prep) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

* If your Slack account uses your @csuchico.edu email, you should be able to search for the workspace and add yourself.
* The Slack phone app is technically optional, but really really helpful/handy. Students historically have stated it's much easier to work with. If you opt out of the phone app, make sure the program is installed onto your laptop. You need to be connected throughout the semester, not just when you remember to log in. 

<br>

# Materials
```{r}
kable(mats) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

# Assignments
```{r}
kable(hw) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

### Data Camp Assignment
* Your goal is to collect around 25,000 XP from any course in Data Camp. This is approximately 5 classes. 
* You have all semester to do so. I will assign midterm progress points around Spring Break. 
* Your past work does not count. 
* I highly recommend that you engage in a skill track to do this.  https://www.datacamp.com/tracks/skill 
* You are not limited to learning R! Use this time to pick up on Python if you like.

----

# Monday: `r topics[1]`

```{r}
kable(mon) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

Rules for producing questions: 

1.	Ask as many questions as you can
2.	Do not stop to answer, judge or to discuss the questions
3.	Write down every question _exactly_ as it is stated
4.	Change any statement into a question


# Wednesday: `r topics[2]`

```{r}
kable(wed) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

### Calling all people with data/projects!
Projects this semester will be user generated. They must entail a sufficient amount of data exploration and modeling, and require some sort of modeling technique that we cover in this class (missing data, spatio-temporal, clustered or correlated data, classification/prediction, multivariate analysis.)

* Graduate research? 
* Senior project? 
* Have an advisor with data/questions to ask and not enough time to investigate?
* The subject field is up to you! It does not have to be biological/natural sciences related. 

Proposers must create a 2-3 minute "elevator pitch" video about their data and project. Post this video on youtube and put the link in the `#projects` Slack channel by Friday.

* Over the weekend, everyone should review the proposals and submit their desired project rankings/preferences that they would like to work on. 
* I will likely post at least one proposal to ensure that there are enough projects to go around. Mine may be the most difficult given that you won't have a subject matter expert as the data owner directly in your group. 

Small teams (2-3) will be formed to work on these projects throughout the semester. 

* I will try my absolute best to assign people to the project they are most interested in. 
    - I will create your own private slack channel for you to collaborate in.  
* The project lead (the person with the data) is responsible for keeping the analysis moving forward, educating their teammates on the scientific context of the research, responsible for the majority of the contextual writing, and will be first author on the poster for the CNS poster session May. 
* Project members are responsible for asking questions to understand the scientific context, providing assistance with programming and analysis, writing the data analysis and results sections of the poster. 

You will mostly work independently on your projects throughout the semester, but there will be some class sessions that are set aside as open work time.  

* There will be one midterm check in presentation during week 8
* And you are to create and present a poster at the College of Natural Sciences poster session. 

# Friday: `r topics[3]`

```{r}
kable(fri) %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```


