---
title: "HW 03 - Missing Data Assignment"
author: "Template"
output:
  html_document: 
    highlight: pygments
    theme: readable
    toc: yes
    toc_float: yes
  pdf_document: default
---

```{r, include=FALSE, warning=FALSE, message=FALSE}
lib <- c("VIM",  "dplyr", "mice", "missForest", "ggplot2", "gridExtra", "knitr", "scales", "lattice", "forestplot", "kableExtra")
invisible(lapply(lib, library, character.only=T))
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
theme_set(theme_bw())
scale_fill_discrete <- scale_fill_viridis_d
```

> THIS FILE WILL NOT KNIT FULLY WITHOUT MODIFICATION OF CODE CHUNKS. SOME ARE SET TO `eval=FALSE` TO NOT THROW ERRORS, AND SOME CODE IS LEFT FOR YOU TO FILL IN. YOU WILL HAVE TO ADDRESS THESE WHEN YOU GET THERE.

> YOU ALSO MUST READ THE INSTRUCTIONS VERY VERY CAREFULLY. THIS TEMPLATE IS NOT A SUBSTITUTE FOR THE INSTRUCTIONS

> DELETE THESE MESSAGES BEFORE YOU SUBMIT YOUR FINAL VERSION.


# Understanding impact of missing data on parameter estimates. 
 
### 1. Simulate and describe the following population distributions. 

```{r}
set.seed(8675309)
N=1000

# sample data from known/named distributions. 
norm.pop.data <- data.frame(x=rnorm(n=N, mean=10, sd=2), dist = "Normal") 
chi2.pop.data <- data.frame(x=rchisq(N,10), dist = "X2")
unif.pop.data <- data.frame(x=runif(N, 0,20 ), dist = "Uniform")

# combine into one data set
pop.data <- rbind(norm.pop.data, chi2.pop.data, unif.pop.data)

# calculate grouped summary stats
pop.ss <- pop.data %>% group_by(dist) %>% 
                    summarise(mean=mean(x), var=var(x), 
                              min=min(x), max=max(x))
kable(pop.ss, digits=3) %>% kable_styling(full_width=FALSE)

# plot pop data - one panel per distribution. 
ggplot(pop.data, aes(x=x, fill=dist)) + geom_histogram()  + 
      geom_vline(data=pop.ss, aes(xintercept=mean), col="darkgreen") +
      geom_text(data=pop.ss, parse=TRUE, hjust=-.5,
                aes(y = 200, x=mean, label= paste("mu == ", round(mean,3)))) + 
      facet_wrap(~dist, ncol=1) + scale_fill_discrete(guide=FALSE)

```

> Write your answer here.



### 2. Set p=20% of values missing completely at random (MCAR), then compare the observed distribution to the population. 

```{r, echo=FALSE}
# don't change this function, and don't set a seed.
create.MCAR <- function(dta, pmiss){ 
    N <- length(dta)
    set.missing.idx <- sample(1:N, size=pmiss*N, replace=FALSE)
    observed.data <- dta[-set.missing.idx] 
    return(observed.data)
}
```

Set values to missing
```{r, eval=FALSE}
# pull sample of n=40
s=40
set.seed(8675309)
norm.samp <- sample(norm.pop.data$x, size=s, replace=TRUE)
chi2.samp <- 
unif.samp <- 

# Create missing (make sure to match the distribution names exactly)
obs.norm <- data.frame(x=create.MCAR(dta=norm.samp, pmiss=.2), dist="Normal")
obs.chi2 <- 
obs.unif <- 

# combine into one data set
observed <- rbind(obs.norm, _________, _________)

# plot population distribution, with sample points added on in black. 
ggplot(pop.data, aes(x=x, fill=dist)) + geom_histogram()  + 
      facet_wrap(~dist, ncol=1) + scale_fill_discrete(guide=FALSE)  + 
      geom_dotplot(data=observed, aes(x=x), dotsize=.5, fill="black")

```

> Write your answer here.

### 3. How does missing data affect inference? How much bias is there? Does the shape of the distribution matter? 

```{r, eval=FALSE}
# calculate grouped summary stats & approx 95% CI's
mcar.ci <- observed %>% group_by(dist) %>% 
                    summarise(xbar=mean(x), 
                              lower = xbar-2*sd(x)/sqrt(n()), 
                              upper = xbar+2*sd(x)/sqrt(n()))

# take the true mean and distribution name from the population summary stats
compare.mcar <- pop.ss %>% select(dist, mean) %>% 
# then left join on the sample CI from the mcar observed data
                    left_join(mcar.ci) %>% 
# calculate the bias, and a logical indicator for if the CI covers the mean. 
                    mutate(abs.bias = xbar-mean, 
                           pct.bias = (abs.bias/mean)*100, 
                           cover = ((mean < upper) & (mean > lower)))

# pretty display
kable(compare.mcar, digits=4) %>% kable_styling(full_width=FALSE)

```

> Write your answer here.

### 4. How does the % missing change the above results? 

```{r}
N=1000
s=100
set.seed(1067)

norm.pop <- data.frame(x=rnorm(n=N, mean=50, sd=2)) 
mu = mean(norm.pop$x)
norm.0   <- data.frame(x=sample(norm.pop$x, size=s, replace=TRUE), dist="0%")

# Create missing
norm.20 <- data.frame(x=create.MCAR(dta=norm.0$x, pmiss=.2), dist="20%")
norm.40 <- data.frame(x=create.MCAR(dta=norm.0$x, pmiss=.4), dist="40%")
norm.60 <- data.frame(x=create.MCAR(dta=norm.0$x, pmiss=.6), dist="60%")
norm.80 <- data.frame(x=create.MCAR(dta=norm.0$x, pmiss=.8), dist="80%")

norm.obs <- rbind(norm.0, norm.20, norm.40, norm.60, norm.80)

norm.mcar.ci <- norm.obs %>% group_by(dist) %>% 
                              summarise(xbar=mean(x), 
                              lower = xbar-2*sd(x)/sqrt(n()), 
                              upper = xbar+2*sd(x)/sqrt(n()))

norm.mcar.ci %>% mutate(abs.bias = xbar-mu, 
                        pct.bias = (abs.bias/mu)*100, 
                        cover = ((mu < upper) & (mu > lower))) %>% 
  kable(digits=4) %>% kable_styling(full_width=FALSE)

ggplot(norm.pop, aes(y=x, x=0)) + 
        # pop stuff first
        geom_violin(fill="grey30") +
        geom_point(aes(x=0, y=mu), pch=17, size=3, col="red") + 
        geom_hline(yintercept=mu) + 
        # now samples
        geom_jitter(data=norm.obs, aes(y=x, x=as.numeric(dist)), width=.08) +
        geom_violin(data=norm.obs, aes(y=x, x=as.numeric(dist), fill=dist), alpha=.3) + 
        stat_summary(data=norm.obs, aes(group=dist, x=as.numeric(dist)),
                     fun.y = 'mean', geom='point', pch=17, size=3, col="red") +
        geom_errorbar(data=norm.obs, aes(y=x, x=as.numeric(dist)), 
                      stat="summary", fun.data="mean_se", col="red",
                      fun.args = list(mult = 2), width=0.3, size=1) + 
        scale_x_continuous(breaks=c(0:5), labels=c("Pop", levels(norm.obs$dist)))  +
        scale_color_viridis_d(guide=FALSE) + scale_fill_viridis_d(guide=FALSE) + 
        xlab("Percent missing") + ylab("")
```

> Write your answer here.

### 5. Repeat problems 2 and 3 using a different missing data mechanism.  

```{r, echo=FALSE}
create.NMAR <- function(pop.data, pmiss){
    observed.data <- pop.data %>% arrange(x) %>% 
                  mutate(prop.miss=seq(0, pmiss, length.out=N), 
                         flag.miss = rbinom(N, 1, prop.miss)) %>%
                  filter(flag.miss==0)
    samp.mean <- mean(observed.data$x) 
    return(samp.mean)
}
```


### 6. What do you think would happen if the missing data mechanism was negatively correlated with the value of x?



# Multiple Imputation using Chained Equations

```{r, eval=FALSE}
hiv.all <- "read your data in here"

hiv <- hiv.all %>% 
       select(age, gender, bsi_overall, frnds, hookey, likesch, school, 
              jobmo, edumo, howrel, attserv, livwith, finsit)
```

### 1. What percent of the data set overall is missing?



  
### 2. How much missing data is there per variable?




### 3. Describe the missing data patterns. 





### 4a. Use tables to examine the relationship in missing data between 1) the two religion variables `howrel` and `attserv`, 2) between the two financial variables `jobmo` and `finsit`, and 3) how much they like school `likesch` and if they have played hookey `hookey`. 






### 4b. Use a margin plot to describe the relationship of missing data between Age and BSI overall.





### 5. Multiply impute this data set $m=5$ times. State the imputation models used for each variable.






### 6. After controlling for other measures, what is the effect of gender on the likelihood a student will skip school? Adjust the model for fit or stability as needed. Report your results in a nice table and interpret the effect of gender on skipping school. 

  
#### 6a. Fit this model on the complete cases (no imputation).









#### 6b. Fit this model on the multiply imputed data sets and report the pooled estimates and intervals. 
Interpret the effect of gender on playing hookey. Did it change from the complete case model? 







### 7. Create a forestplot to compare the results for all coefficients in the model. 

What are the biggest differences you notice? Would the inference/interpretation of the effect of any covariate on the odds of a student skipping school change depending on what model you use? 

```{r, fig.height=12, fig.width=10}

```


